\label[sec:rgb]
\sec Extraction of Features from RGB images

The sequence of RGB images is captured with the xtion camera (chap.~\ref[secc:camera]). Images have resolution 640$\times$480~px (width$\times$height). RGB images are stored in the "bagfile"s like single row vector. After loading data into MATLAB~(chap.~\ref[sec:loadToMatlab]) data are converted from row representation to three-dimensional RGB intensity representation ${\bf I}_{u,v}$ of images with dimensions 480$\times$640~px ($m\times n$), where ${\bf I}_{u,v}=[~{r}(u,v),~{g}(u,v),~{b}(u,v)~]$, $u \in 1,2,\dots ,m$, $v \in 1,2,\dots,n$. ${r}(u,v)$, ${g}(u,v)$ and ${b}(u,v)$ are function of brightness of pixel on the coordinates $u,v$ and each of ${r}(u,v)$, ${g}(u,v)$ and ${b}(u,v)$ represents are relevant intensity of single color from the RGB color-space.
Unless specified otherwise, the computations are always carried for each ${r}(u,v)$, ${g}(u,v)$ and ${b}(u,v)$ separately.
Raw RGB data are shown in the figure~\ref[fig:extRGB].

\medskip \clabel[fig:extRGB]{Sample RAW RGB images}
\picw=18cm 
%\centerline {\inspic pictures/todo.pdf \hfil\hfil \inspic pictures/todo.pdf }\nobreak
%\centerline {a)\hfil\hfil b)}\nobreak\medskip
%\centerline {\inspic pictures/todo.pdf \hfil\hfil \inspic pictures/todo.pdf }\nobreak
%\centerline {c)\hfil\hfil d)}\nobreak\medskip
\cinspic pictures/rgbsample.pdf
\caption/f Sample of RAW RGB images.
\medskip

%\secc Rectification of RGB images

%		\Green
%		\begitems \style o
%			* Popsat, jak opravím RGB snímek + obrázek
%		\enditems
%		\Black

\label[secc:bagSubRGB]
\secc Background Subtraction

In the chapter~\ref[sec:captureBackground] is described a way of capturing background image. Respectively was not captured a single image, but was captured a sequence of $N$ images ${\bf F}^{i}=\{{\bf F}^{1},{\bf F}^{2},\dots,{\bf F}^{N}\}$ in the time $i \in \{1,2,\dots,N\}$, where ${\bf F}^i_{u,v}=[{r}(u,v),~{g}(u,v),~{b}(u,v)~]$.
The~sequence of background images ${\bf F}^i_{u,v}$ is averaged to ${\overline{\bf F}}_{u,v}=[{r}(u,v),~{g}(u,v),~{b}(u,v)]$ according to~\ref[eq:averageRGB]. Together with mean value ${\overline{\bf F}}_{u,v}$ of RGB background images, is computed corrected sample standard deviation ${\bf \sigma}_{u,v}=[~{\sigma_{R}}(u,v),~{ \sigma_{G}}(u,v),~{\sigma_{B}}(u,v)~]$~\ref[eg:deviationRGB], whith is used like intensity threshold.
\label[eq:averageRGB]$$
\forall u, v :  {\overline{\bf F}}_{u,v} = \sum_{i=1}^{N} {{{\bf F}^i_{u,v}}\over{N}} \eqmark
$$
\label[eg:deviationRGB]$$
\forall u, v :  {\bf \sigma}_{u,v}=\sqrt{{1\over {N-1}} \sum_{i=1}^{N} \left( {\bf F}^i_{u,v} - {\overline{\bf F}}_{u,v} \right)^2} \eqmark
$$

From the RGB image ${\bf I}$ is computed a binary silhouette image $s(u,v)$ according to~\ref[eq:backgroundSubtraction],where $\alpha > 1$ is a threshold coeficient.
\label[eq:backgroundSubtraction]
$$
\forall u, v :
{s}(u,v) =
\cases{
1, &if $
\cases{
&$
\left| {r}(u,v) - {\overline{\bf F}}_{R}(u,v)\right| >  \alpha \thinspace {\bf \sigma}_{R}(u,v)
$;\cr
{\rm or} &$
\left| {g}(u,v) - {\overline{\bf F}}_{G}(u,v)\right| >  \alpha \thinspace {\bf \sigma}_{G}(u,v)
$;\cr
{\rm or} &$
\left| {b}(u,v) - {\overline{\bf F}}_{B}(u,v)\right| >  \alpha \thinspace {\bf \sigma}_{B}(u,v)
$;\cr
}
$\cr
0, &otherwise. 
\cr}
\eqmark
$$

Silhouette images are shown in the figure~\ref[fig:rgbsub].

\medskip \clabel[fig:rgbsub]{Background subtraction of RGB images}
\picw=18cm 
\cinspic pictures/subtracked.pdf
\caption/f Sample of binary silhouette images - background subtraction.
\medskip

The figure~\ref[fig:rgbsub] shows that background subtraction is not perfect. This imperfection have two main reasons. First reason is that the the gripper of arm "r1" and the surrounding of monochrome background are partly seen in the image. This would not be a problem for our method, if these objects have not a shiny finish, which reflects the garment when the garment is moving. By experimental results, we found that the garment moves only against a monochrome background and not enter the background surroundings during the entire movement. This imperfection is removed with help of a clipping mask, which cover gripper and monochrome background surrounding.

Second reason is a noise on the RGB image and tiny changes of brightness of pictures, which is caused by the garment movement. This imperfection is removed with help of morphological operation {\bf opening}. Because this imperfection may occur in reverse too, ie so that the point of the garment is detected as a background thus {\bf closing} operation followed opening operation (mean of these morpholigical operation is explained in~\cite[hlavac2008] p.667-669). We use for this operations the MATLAB functions "imopen()" and "imclose()".

\medskip \clabel[fig:rgbsubmorph]{Background subtraction of RGB images after morphological operation}
\picw=18cm 
\cinspic pictures/rgbsub.pdf
\caption/f Background subtraction of RGB images after morphological operation.
\medskip


%\secc Finding End of Gripper

%		\Green
%		\begitems \style o
%			* Popsat, jak naleznu oblast, kterou opisuje chapadlo při hýbání s látkou a jak z tohoto pohybu naleznu konec chapadlo v obraze
%			* Obrázek s vyznačenou kružnicí a bodem jako koncem gripperu
%		\enditems
%		\Black

\secc Finding Major Axis of the Garment and Remove Gripper

For further image processing, we must be sure that we have only one image object in the binary silhouette image. We assume that the garment is the largest object in the image. We use MATLAB functions "bwconncomp ()", which finds all objects in an image. For these object is individually calculated their size.  Subsequently, according to these sizes determine the largest object and throw away the rest. The detailed explanation of these region identification is described in the~\cite[hlavac2008]~(p.332).

In the next step we found major and minor axis of the garment. Befere we can find these parameters we have to remove from the image a showed end of the gripper. We have captured images without measured garment in the gripper, thus we can find an area in which the gripper is. Then this part of the image is removed from the image of the measured garment. A better way would be to compare the captured image data from a simulated robot model in an environment of ROS.

After the gripper was removed from the gripper, the major and minor axis could be found by using the spatial moments (described in~\cite[haralock1991computer] p.74,658). This method describes finding major and minor axis for an ellipse (reasons are described below in the chap.~\ref[secc:centralCurve]). The axes are found using MATLAB functions "regionprops()" which gave us center of the object, lenght of major and minor axis and clockwise orientation of the major axis.
Founded major and minor axes of the silhouette of the garment and subtraced images without the gripper are shown in the figure~\ref[fig:rgbsub].

\medskip \clabel[fig:rgbminoraxes]{Major and minor axes of the silhouette}
\picw=18cm 
\cinspic pictures/gripperMainAxisRGB.pdf
\caption/f Sample of major and minor axes of the silhouette of the garment and subtraced images without the gripper.
\medskip

\label[secc:centralCurve]
\secc Finding Central Curve of the Garment

To obtain the garment parameters, we decided to track a central curve of the garment (central curve of the silhouette). During this project we have tried various methods of finding the curve, for example, the average pixel with respect to the y-axis, or find a skeleton of the silhouette image (\cite[hlavac2008],~p.365). Search skeleton of the silhouette image it seemed like the most promising from the beginning, but finally there was a problem in the form of determining the curve at the ends of the garment.

Finally, we chose finding of the central curve so that the search for the centers of the lines, which are perpendicular to the major axis of the garment (silhouettes) and theirs endpoints belong to the outline of the silhouettes.

The first step to obtaining the central curve of the silhouette is finding the the outline of the silhouette. To achieve the outline, we use the edge detector. We chose the edge detector, which uses sobel operator (explain in~\cite[hlavac2008],~p.136). Edge of the silhouette is shown in the figure~\ref[fig:rgbedge].

\medskip \clabel[fig:rgbedge]{Edge of the silhouette}
\picw=18cm 
\cinspic pictures/silhouette.pdf
\caption/f Sample of edge of the silhouette of the garment.
\medskip

\medskip \clabel[fig:centerSil]{Sample of founded center curve of the silhouette}
\picw=7cm 
\centerline {\inspic pictures/todo.pdf \hfil\hfil \inspic pictures/todo.pdf }\nobreak
\centerline {a)\hfil\hfil b)}\nobreak\medskip
\centerline {\inspic pictures/todo.pdf \hfil\hfil \inspic pictures/todo.pdf }\nobreak
\centerline {c)\hfil\hfil d)}\nobreak\medskip
%\cinspic pictures/rgbsample.pdf
\caption/f Sample of founded center curve of the silhouette.
\medskip

\secc Finding Mathematical Features from RGB images

To estimate the parameters of the garment, we wanted to use the points of the central curve of the silhouette over time.
Unfortunately, the position of the points forming the central curve is not only influenced by movement of the garment, but is strongly influenced by the shape of the silhouette. Moreover, the method of background subtraction needs monochrome background to proper functioning. So we decided not to use RGB images to estimate the parameters of the garment.



		\Green
		\begitems \style o
			* Napsat, jak hledám osu bramboroidu
			* Popsat zde zavrhnuté metody
			\begitems \style o
				* Kostra grafu + obrázky + proč jsem to nepoužil
				* Střed dle y osy + obrázek + proč jsem to nepoužil
			\enditems
			* Obrázky postupného nalezení osy bramborouidu (při aproximaci udělat více obrázků)
		\enditems
		\Black

		\Green
		\begitems \style o
			* Popsat, jak z osy bramboroidu naleznu body, které předávám jako výstup
			* Obrázky se siluetou a v ní s body
		\enditems
		\Black

